MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex

\section{Conclusions}

>>>>

\section{Conclusions}
Our work shows that a Bluetooth keylogger is possible to do. We successfully forwarded packets from the keyboard to the victim with no delay. Accomplishing this task was easier said than done. We had to use several software packages in the correct order to get the behaviors we wanted. The main conclusion we came away with is that Bluetooth is needlessly complex. The API is horrible and underdeveloped. Which was not explained by any documentation we found. The documentation was useless and led us in the wrong direction 99\% of the time. If anyone could improve Bluetooth in any way we recommend making the API cleaner and standardized and improving the documentation that goes with it.
